Notes on 10d Super Yang-Mills

### 2019-03-01 10d_SYM_Notes.tex
Starting to define minimal 10d SYM

\section{Minimal Super Yang-Mills}
Our starting point will be the theory complexifying the usual 10d super Yang-Mills theory.  Fix a complex reductive gauge group $G$ with Lie algebra $\gg$.  The ordinary fields of super Yang-Mills theory on $\RR^{10}$ consist of a boson: a connection $A$ on the trivial $G$-bundle, and a fermion: a $\gg$-valued section $\lambda$ of the Weyl spinor bundle associated to the spinor representation $S_+$ \footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of the Majorana-Weyl spinor bundle, which necessitates working in Lorentzian signature.}.  These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{10}$.

@@

We can re-encode this data in terms of the classical BV complex.  This is the $L_\infty$-algebra whose underlying cochain complex takes the form
\[\xymatrix{
\Omega^0(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{10}; \gg) \ar[r]^{\d \ast \d} &\Omega^9(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^{10}(\RR^{10}; \gg) \\
&\Omega^0(\RR^{10}; \Pi S_- \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{10}(\RR^{10}; \Pi S_- \otimes \gg), &
}\]
with degree $-3$ invariant pairing induced by the invariant pairing on $\gg$ and the pairing $(,)$ between $S_+$ and $S_-$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{10}; \gg)$ on everything along with
\begin{align*}
\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^0(\RR^{10}; S_{+} \otimes \gg) &\to \Omega^{10}(\RR^{10}; S_{-} \otimes \gg) \\
(A \otimes \lambda) &\mapsto \ast \sd A \lambda
\end{align*}
in degree 2, and the map
\begin{align*}
\ell_3 \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
\end{align*}
in degree 3.

>>>>

\section{Minimal Super Yang-Mills}
Our starting point will be the theory complexifying the usual 10d super Yang-Mills theory.  Fix a complex reductive gauge group $G$ with Lie algebra $\gg$.  The ordinary fields of super Yang-Mills theory on $\RR^{10}$ consist of a boson: a connection $A$ on the trivial $G$-bundle, and a fermion: a $\gg$-valued section $\lambda$ of the Weyl spinor bundle associated to the spinor representation $S_+$ \footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of the Majorana-Weyl spinor bundle, which necessitates working in Lorentzian signature.  I think for our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.  The complexified theory twists to holomorphic Chern-Simons theory with complex gauge group.}.  These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{10}$.

@@

We can re-encode this data in terms of the classical BV complex (Phil and I wrote this down in \cite[Section 3.1]{ElliottYoo1}).  This is the $L_\infty$-algebra whose underlying cochain complex takes the form
\[\xymatrix{
\Omega^0(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{10}; \gg) \ar[r]^{\d \ast \d} &\Omega^9(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^{10}(\RR^{10}; \gg) \\
&\Omega^0(\RR^{10}; \Pi S_- \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{10}(\RR^{10}; \Pi S_- \otimes \gg), &
}\]
with degree $-3$ invariant pairing induced by the invariant pairing on $\gg$ and the pairing $(,)$ between $S_+$ and $S_-$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{10}; \gg)$ on everything along with
\begin{align*}
\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^0(\RR^{10}; S_{+} \otimes \gg) &\to \Omega^{10}(\RR^{10}; S_{-} \otimes \gg) \\
(A \otimes \lambda) &\mapsto \ast \sd A \lambda
\end{align*}
in degree 2, and the map
\begin{align*}
\ell_3 \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
\end{align*}
in degree 3.
